The \dealii Library, Version 9.2

### 2020-05-13 9.2/paper.tex
update
Make a bit of progress on the release paper.

@@

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
%     Ross Maguire Kynch,
%     Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

The major changes of this release are:
%
\begin{itemize}
\item
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}),
%   \item Dedicated support for symbolic algebra (see
%     Section~\ref{subsec:sd}),
%   \item Full support for $hp$~adaptivity in parallel computations (see
%     Section~\ref{subsec:hp}),
%   \item An interface to the HDF5 file format and libraries (see
%     Section~\ref{subsec:hdf5}),
%   \item Significantly extended GPU support (see Section~\ref{subsec:gpu}),
%   \item Parallel geometric multigrid (GMG) improvements (see
%     \cite{ClevengerHeisterKanschatKronbichler2019} and
%     Section~\ref{subsec:gmg}),
%   \item Four new tutorial programs (step-61, step-62, step-63, step-64),
%     as well as one new code gallery program (see
%     Section~\ref{subsec:steps}).
\end{itemize}
%
The major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item
% \item
%   The release contains a number of performance improvements and bug fixes for
%   the matrix-free framework. One notable improvement is the support for
%   renumbering of degrees of freedom within the cells for discontinuous
%   elements, avoiding some reshuffling operations across the SIMD lanes
%   with vectorization over several cells and faces, which is especially
%   useful on processors with AVX-512 vectorization (8 doubles), speeding up
%   operations by up to 10\%. Secondly, the strategy for the most efficient
%   tensor product evaluators according to the performance analysis of
%   \cite{KronbichlerKormann2019} in the context of more quadrature points than
%   shape functions has been revised for better performance.
%
% \item A new class \texttt{ParsedConvergenceTable} has been introduced
%   that greatly simplifies the construction of convergence tables,
%   reading the options for the generation of the table from a parameter
%   file, and providing methods that, combined with a parameter file,
%   allow one to generate convergence tables using one-liners in user
%   codes.
%
% \item
%   The \texttt{FE\_BernardiRaugel} class implements the non-standard
%   Bernardi-Raugel (BR) element that can be used to construct a stable
%   velocity-pressure pair for the Stokes equation \cite{BR85}. The BR
%   element is an enriched version of the $Q_1^d$ element with added bubble
%   functions on each edge (in 2d) or face (in 3d). It addresses the fact
%   that the $Q_1^d\times Q_0$ combination is not inf-sup stable (requiring a
%   larger velocity space), and that the $Q_2^d\times Q_0$ combination is
%   stable but converges with only first-order at the cost of the large
%   number of velocity unknowns. The BR space is thus intermediate between the
%   $Q_1^d$ and $Q_2^d$ spaces.
%
%   The element is currently only implemented for parallelogram meshes due to
%   difficulties associated with the mapping of shape functions: The shape
%   functions of the $Q_1^d$ part of the element need to be mapped as
%   scalars, as is common for the vector components of the $Q_1^d$ element;
%   on the other hand, the vector-valued edge bubble functions need to be
%   mapped using the Piola transform as is common for the Raviart-Thomas
%   element. \dealii{} does not currently have the ability to use different
%   mappings for individual shape functions, though this functionality is
%   planned for the next release.
%
% \item
%   The \texttt{FE\_NedelecSZ} class is a new implementation of the
%   N{\'e}d{\'e}lec element on quadrilaterals and hexahedra. It is based on
%   the work of Zaglmayr \cite{Zag06} and overcomes the sign conflict issues
%   present in traditional N{\'e}d{\'e}lec elements that arise from the edge
%   and face parameterizations used in the basis functions. Therefore, this
%   element should provide consistent results for general quadrilateral and
%   hexahedral elements for which the relative orientations of edges and
%   faces (as seen from all adjacent cells) are often difficult to establish.
%   The \texttt{FE\_NedelecSZ} element addresses the sign conflict problem by
%   assigning a globally defined orientation to local edges and faces. A
%   detailed overview of the implementation of the \texttt{FE\_NedelecSZ}
%   element in \dealii{} can be found in \cite{Kynch2017}.
%
% \item All of the elementary geometrical objects of the library (namely
%   \texttt{Point<dim>}, \texttt{Segment<dim>}, and
%   \texttt{BoundingBox<dim>}) have been augmented with the traits
%   needed to comply with \texttt{boost::geometry} concepts. A new
%   interface to \texttt{boost::geometry::index::rtree} has been added
%   that simplifies the construction of spatial indices based on points,
%   bounding boxes, or segments.
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{bla1}
\label{subsec:bla1}

@@

In addition, there are seven new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\item \texttt{step-50}
\item \texttt{step-58}
\item \texttt{step-65}
\item \texttt{step-67}
\item \texttt{step-69}
\item \texttt{step-70}
\end{itemize}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 15 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item
% \item The \texttt{VectorView} class was removed. We recommend either copying the
%       vector subset into a \texttt{Vector} or using a \texttt{BlockVector}.
% \item The function \texttt{Subscriptor::subscribe()}, used through the
%   \texttt{SmartPointer} class, now requires a pointer to a
%       \texttt{std::atomic<bool>} that tracks whether or not the pointer to the
%       subscribed-to object is still valid.
% \item The \texttt{ConstraintMatrix} class gained a template parameter for the scalar
%       type and was been renamed \texttt{AffineConstraints}. Several methods that
%       take vectors or matrices as arguments,
%       such as \texttt{AffineConstraints::distribute\_local\_to\_global()},
%       now require that all matrix and vector arguments have matching number
%       types.
% \item Similarly, the functions \texttt{create\_mass\_matrix} and
%       \texttt{create\_boundary\_mass\_matrix} in the \texttt{MatrixCreator}
%       namespace no longer
%       support matrix and vector objects of different types.
\end{itemize}

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 5/11/2020 MM - TODO: remove authors of paper
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Martin Kronbichler,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

>>>>

\usepackage{todonotes}

@@

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}), 
\end{itemize}
%
The major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item x \todo[inline]{Wolfgang to write about complex-valued output}
\item y \todo[inline]{Timo to write about problems and fixes for
  computations with more than $2^{32}$ unknowns}
\item z \todo[inline]{What else?}
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

@@

@@

In addition, there are seven new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\todo[inline]{Zhuoran to write}
\item \texttt{step-50}
\todo[inline]{Timo/Conrad/... to write}
\item \texttt{step-58}
\todo[inline]{Wolfgang to write}  
\item \texttt{step-65}
\todo[inline]{Martin to write}  
\item \texttt{step-67}
\todo[inline]{Martin to write}  
\item \texttt{step-69}
\todo[inline]{Matthias/Ignacio to write}  
\item \texttt{step-70}
  \todo[inline]{Also need to update announce and announce-short if this
    makes it into the release.}
\end{itemize}

\todo[inline]{Do we have new code gallery programs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for large, fully distributed meshes}
\label{subsec:pfT}

\todo[inline]{Peter: Write something about p::f::T}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Better support for parallel $hp$-adaptive algorithms}
\label{subsec:hp}

\todo[inline]{Marc: Your section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for particle-based methods}
\label{subsec:particles}

\todo[inline]{Luca: Your section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Python interfaces}
\label{subsec:python}

\todo[inline]{What's new here? mention step-49 and step-53 versions written in python.}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item
\end{itemize}

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 5/11/2020 MM
\todo[inline]{TODO: remove authors of paper}
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Martin Kronbichler,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.
